Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-23 analysis/paper/paper.Rmd
edits to intro

<!--burial study- network analysis-->
Burials contains valuable information of both individual mortuary practices and the structure of a society inherited in burial relations. With the development of network science and graph theory, studying relations among burials and exploring its social implication become promising [@Sosna2013]. Mortuary practices such as burial forms, grave goods, and related ritual practices could represent the social relations between individuals, allowing the inference for social structures. This enables the study of social differences based on burials to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For examples, the use of burial goods can reflect social practices in a broader of cultural contexts to present personal wealth, social roles, or a traditional custom. Burials with grave goods in common often indicate some underlying social relations connected through trade, exchange, and gifting [@Coward2013, pp. 252]. Identifying the structure of relationships among burials can give an insight to the structure of a social organization. One common way to study connections between individuals is network analysis, which has been applied increasingly to archaeological studies in recent years [@Mills2017]. Networks are represented as graphs consisting of a set of actors, such as people, groups, or organizations, and a set of links connecting them [@Brughmans2018; @Robins2007]. Technically speaking, actors are "nodes" connected by multiple "edges", representing relationships, between nodes. The basic unit of relationship is called dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, indicating social relations in societies [@Marin2011]. With network analysis, we can quantify, visualize, and statistically test hypotheses of the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. The application in archaeology is widely used for different topics including distribution of archaeological sites, grave goods, and social complexity [@Coward2013; @Mizoguchi2013; @Potgieter2008]

>>>>

<!--burial study- network analysis-->
Burials contain valuable information about both individual mortuary practices and the structure of a society. The development of network science and graph theory provides many new tools for the study of the relations between burials and exploration their social implications [@Sosna2013]. Mortuary practices such as burial forms, grave goods, and related ritual practices that structure the material configuration of burials can represent social relations between members of a community, allowing the inference for social structures [citation needed]. This means we can use data from burials to study social differences to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For example, burial goods can reflect social practices in broader cultural contexts to represent personal wealth, social roles, or traditional customs. Burials with grave goods in common often indicate some similar underlying social relations, for example, individuals that share similar access to trade, exchange, and gifting networks [@Coward2013, pp. 252]. Identifying the structure of relationships among burials can give insights into the structure of social organization.

One common way to study connections between individuals is network analysis, which has been increasingly applied by archaeologists in recent years [@Mills2017]. Networks are represented as graphs consisting of a set of actors, such as people, groups, or organizations, and a set of links connecting them [@Brughmans2018; @Robins2007]. <!-- define 'links' a bit more --> Actors are "nodes" connected by multiple "edges", representing relationships, between nodes. The basic unit of relationship is called a dyad, defined as a connection between two distinct actors [@Lee2016]. In archaeology, relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, indicating social relations in societies [@Marin2011]. With network analysis, we can quantify, visualize, and statistically test hypotheses about the relationships between actors to examine the structure of network and major factors that affect the formation of the structure [@Freeman2004; @Salvini2010]. Network analysis in archaeology is widely used for different topics including distribution of archaeological sites, grave goods, and social complexity [@Coward2013; @Mizoguchi2013; @Potgieter2008]
